---
title: "coling2024_loess_curves"
author: "Amber Converse"
date: "2024-09-11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
library(ggplot2)
library(tidyverse)
library(grid)
library(gridExtra)
```

```{r kruskal_wallis_en}
df <- read_csv("sentence_level/base_measurements/en_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(2,19),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]
general_es_df <- general_df[grepl("es_|en_general", general_df$lang), ]
general_ar_df <- general_df[grepl("ar_|en_general", general_df$lang), ]

genre_df <- long_df[grepl("genre", long_df$lang), ]
genre_es_df <- genre_df[grepl("es_|en_genre", genre_df$lang), ]
genre_ar_df <- genre_df[grepl("ar_|en_genre", genre_df$lang), ]

general_es_df$lang <- ordered(general_es_df$lang,
                              levels=c("en_general_rarity",
                              "es_en_DEEP_general_rarity",
                              "es_en_DEEPL_general_rarity",
                              "es_en_GOOGLE_general_rarity",
                            "es_en_TRANSFORMERS_general_rarity"))
general_ar_df$lang <- ordered(general_ar_df$lang,
                              levels=c("en_general_rarity",
                              "ar_en_DEEP_general_rarity",
                              "ar_en_DEEPL_general_rarity",
                              "ar_en_GOOGLE_general_rarity",
                            "ar_en_TRANSFORMERS_general_rarity"))
genre_es_df$lang <- ordered(genre_es_df$lang,
                              levels=c("en_genre_rarity",
                              "es_en_DEEP_genre_rarity",
                              "es_en_DEEPL_genre_rarity",
                              "es_en_GOOGLE_genre_rarity",
                            "es_en_TRANSFORMERS_genre_rarity"))
genre_ar_df$lang <- ordered(genre_ar_df$lang,
                              levels=c("en_genre_rarity",
                              "ar_en_DEEP_genre_rarity",
                              "ar_en_DEEPL_genre_rarity",
                              "ar_en_GOOGLE_genre_rarity",
                            "ar_en_TRANSFORMERS_genre_rarity"))

group_by(general_es_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )
group_by(general_ar_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )
group_by(genre_es_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )
group_by(genre_ar_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )

pairwise.wilcox.test(general_es_df$rarity, general_es_df$lang, p.adjust.method = "BH")
pairwise.wilcox.test(general_ar_df$rarity, general_ar_df$lang, p.adjust.method = "BH")
pairwise.wilcox.test(genre_es_df$rarity, genre_es_df$lang, p.adjust.method = "BH")
pairwise.wilcox.test(genre_ar_df$rarity, genre_ar_df$lang, p.adjust.method = "BH")
```
Summary of Significance Wilcox Pairwise Test on Rarity:\\
General:
es->en Deep < en (p < 0.0001)
es->en DeepL < en (p < 0.0001)
es->en GT < en (p < 0.0001)
es->en OPUS < en (p < 0.00001)

ar->en Deep < en (p < 0.0001)
ar->en DeepL < en (p < 0.03)
ar->en GT < en (p < 0.001)
ar->en OPUS < en (p < 0.0001)

Genre:
es->en Deep < en (p < 0.0001)
es->en DeepL < en (p < 0.0001)
es->en GT < en (p < 0.0001)
es->en OPUS < en (p < 0.00001)

ar->en Deep < en (p < 0.0001)
ar->en DeepL < en (p < 0.0001)
ar->en GT < en (p < 0.0001)
ar->en OPUS < en (p < 0.0001)

```{r kruskal_wallis_es}
df <- read_csv("sentence_level/base_measurements/es_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(2,11),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

genre_df <- long_df[grepl("genre", long_df$lang), ]

general_df$lang <- ordered(general_df$lang,
                           levels=c("es_general_rarity",
                           "en_es_DEEP_general_rarity",
                           "en_es_DEEPL_general_rarity",
                           "en_es_GOOGLE_general_rarity",
                           "en_es_TRANSFORMERS_general_rarity"))
genre_df$lang <- ordered(genre_df$lang,
                           levels=c("es_genre_rarity",
                           "en_es_DEEP_genre_rarity",
                           "en_es_DEEPL_genre_rarity",
                           "en_es_GOOGLE_genre_rarity",
                           "en_es_TRANSFORMERS_genre_rarity"))

group_by(general_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )
group_by(genre_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )

pairwise.wilcox.test(general_df$rarity, general_df$lang, p.adjust.method = "BH")
pairwise.wilcox.test(genre_df$rarity, genre_df$lang, p.adjust.method = "BH")
```

General:
en->es Deep > es (p < 0.0001)
en->es DeepL > es (p < 0.0001)
en->es GT > es (p < 0.0001)
en->es OPUS > es NOT SIGNIFICANT (p>0.9!!!)

Genre:
en->es Deep > es NOT SIGNIFICANT
en->es DeepL > es NOT SIGNIFICANT
en->es GT > es NOT SIGNIFICANT
en->es OPUS < es  (p < 0.0001)

```{r kruskal_wallis_ar}
df <- read_csv("sentence_level/base_measurements/ar_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(2,11),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

genre_df <- long_df[grepl("genre", long_df$lang), ]

general_df$lang <- ordered(general_df$lang,
                           levels=c("ar_general_rarity",
                           "en_ar_DEEP_general_rarity",
                           "en_ar_DEEPL_general_rarity",
                           "en_ar_GOOGLE_general_rarity",
                           "en_ar_TRANSFORMERS_general_rarity"))
genre_df$lang <- ordered(genre_df$lang,
                           levels=c("ar_genre_rarity",
                           "en_ar_DEEP_genre_rarity",
                           "en_ar_DEEPL_genre_rarity",
                           "en_ar_GOOGLE_genre_rarity",
                           "en_ar_TRANSFORMERS_genre_rarity"))

group_by(general_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )
group_by(genre_df, lang) %>% 
  summarize(
    mean = mean(rarity, na.rm = TRUE),
    sd = sd(rarity, na.rm = TRUE),
    median = median(rarity, na.rm = TRUE),
    IQR = IQR(rarity, na.rm = TRUE)
  )

pairwise.wilcox.test(general_df$rarity, general_df$lang, p.adjust.method = "BH")
pairwise.wilcox.test(genre_df$rarity, genre_df$lang, p.adjust.method = "BH")
```

General:
en->ar Deep < ar (p < 0.0001)
en->ar DeepL < ar (p < 0.0001)
en->ar GT < ar (p < 0.0001)
en->ar OPUS < ar (p < 0.002)

Genre:
en->ar Deep < ar (p < 0.0001)
en->ar DeepL < ar (p < 0.0001)
en->ar GT < ar (p < 0.0001)
en->ar OPUS < ar (p < 0.0001)

```{r loess_curves_complete}
df <- read_csv("sentence_level/base_measurements/en_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(3,19),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]
general_es_df <- general_df[grepl("es_|en_general", general_df$lang), ]
general_ar_df <- general_df[grepl("ar_|en_general", general_df$lang), ]

general_es_df$lang <- ordered(general_es_df$lang,
                              levels=c("es_en_DEEP_general_rarity",
                              "es_en_DEEPL_general_rarity",
                              "es_en_GOOGLE_general_rarity",
                            "es_en_TRANSFORMERS_general_rarity"))
general_ar_df$lang <- ordered(general_ar_df$lang,
                              levels=c("ar_en_DEEP_general_rarity",
                              "ar_en_DEEPL_general_rarity",
                              "ar_en_GOOGLE_general_rarity",
                            "ar_en_TRANSFORMERS_general_rarity"))

p1 <- ggplot(general_ar_df, aes(x=en_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  geom_smooth(method="loess", size=1.5) +
  labs(title="Arabic to English", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("Deep", "DeepL",
                              "GT", "OPUS")) +
  geom_abline(intercept = 0, slope = 1, color="red", linetype="dashed", size=1) +
  theme_minimal()
p2 <- ggplot(general_es_df, aes(x=en_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  geom_smooth(method="loess", size=1.5) +
  labs(title="Spanish to English", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("Deep", "DeepL",
                              "GT", "OPUS")) +
  geom_abline(intercept = 0, slope = 1, color="red", linetype="dashed", size=1) +
  theme_minimal()

df <- read_csv("sentence_level/base_measurements/es_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(3,11),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

p3 <- ggplot(general_df, aes(x=es_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  geom_smooth(method="loess", size=1.5) +
  labs(title="English to Spanish", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("Deep", "DeepL",
                              "GT", "OPUS")) +
  geom_abline(intercept = 0, slope = 1, color="red", linetype="dashed", size=1) +
  theme_minimal()

df <- read_csv("sentence_level/base_measurements/ar_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(3,11),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

p4 <- ggplot(general_df, aes(x=ar_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  geom_smooth(method="loess", size=1.5) +
  labs(title="English to Arabic", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("Deep", "DeepL",
                              "GT", "OPUS")) +
  geom_abline(intercept = 0, slope = 1, color="red", linetype="dashed", size=1) +
  theme_minimal()

grid.arrange(p1, p2, p3, p4, nrow=2, top=textGrob("Native Rarity vs. MT Rarity",gp=gpar(fontsize=20,font=3)))
```

```{r loess_curves_en}
df <- read_csv("sentence_level/base_measurements/en_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(3,19),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

genre_df <- long_df[grepl("genre", long_df$lang), ]

ggplot(general_df, aes(x=en_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  stat_smooth(method="loess") +
  labs(title="Native Rarity vs. MT Rarity", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("ar->en (Deep)", "ar->en (DeepL)",
                              "ar->en (GT)", "ar->en (OPUS)",
                              "es->en (Deep)", "es->en (DeepL)",
                              "es->en (GT)", "es->en (OPUS)"))
```

```{r loess_curves_es}
df <- read_csv("sentence_level/base_measurements/es_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(3,11),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

genre_df <- long_df[grepl("genre", long_df$lang), ]

ggplot(general_df, aes(x=es_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  stat_smooth(method="loess") +
  labs(title="Native Rarity vs. MT Rarity", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("en->es (Deep)", "en->es (DeepL)",
                              "en->es (GT)", "en->es (OPUS)"))
```

```{r loess_curves_ar}
df <- read_csv("sentence_level/base_measurements/ar_rarity.csv")

long_df <- df %>% 
  pivot_longer(
    cols = seq.int(3,11),
    names_to = "lang",
    values_to = "rarity"
  )

general_df <- long_df[grepl("general", long_df$lang), ]

genre_df <- long_df[grepl("genre", long_df$lang), ]

ggplot(general_df, aes(x=ar_general_rarity, y=rarity,
                       group=lang, color=lang)) +
  stat_smooth(method="loess") +
  labs(title="Native Rarity vs. MT Rarity", x="Native Rarity",
       y="MT Rarity", color="Translation Type") +
  scale_color_hue(labels=c("en->ar (Deep)", "en->ar (DeepL)",
                              "en->ar (GT)", "en->ar (OPUS)"))
```

```{r en_rarity_over_time}

df <- read_csv("corpus_level/rarity_different_vocab_sizes_summary.csv")

df <- df[, c("val", "en_general_rarity",
             "es_en_DEEP_general_rarity", 
             "es_en_DEEPL_general_rarity",
             "es_en_GOOGLE_general_rarity",
             "es_en_TRANSFORMERS_general_rarity",
             "ar_en_DEEP_general_rarity",
             "ar_en_DEEPL_general_rarity",
             "ar_en_GOOGLE_general_rarity",
             "ar_en_TRANSFORMERS_general_rarity")]

ggplot(df, aes(x=val)) +
  geom_line(aes(y=en_general_rarity, color="Native")) +
  geom_line(aes(y=es_en_DEEP_general_rarity, color="es->en (Deep)")) +
  geom_line(aes(y=es_en_DEEPL_general_rarity, color="es->en (DeepL)")) +
  geom_line(aes(y=es_en_GOOGLE_general_rarity, color="es->en (GT)")) +
  geom_line(aes(y=es_en_TRANSFORMERS_general_rarity, color="es->en (OPUS)")) +
  geom_line(aes(y=ar_en_DEEP_general_rarity, color="ar->en (Deep)")) +
  geom_line(aes(y=ar_en_DEEPL_general_rarity, color="ar->en (DeepL)")) +
  geom_line(aes(y=ar_en_GOOGLE_general_rarity, color="ar->en (GT)")) +
  geom_line(aes(y=ar_en_TRANSFORMERS_general_rarity, color="ar->en (OPUS)")) +
  labs(title="Common Vocab Size vs. General Rarity",
       x="Common Vocab Size",
       y="General Rarity",
       color="Language")
```
```{r es_rarity_over_time}

df <- read_csv("corpus_level/rarity_different_vocab_sizes_summary.csv")

df <- df[, c("val", "es_general_rarity",
             "en_es_DEEP_general_rarity", 
             "en_es_DEEPL_general_rarity",
             "en_es_GOOGLE_general_rarity",
             "en_es_TRANSFORMERS_general_rarity")]

ggplot(df, aes(x=val)) +
  geom_line(aes(y=es_general_rarity, color="Native")) +
  geom_line(aes(y=en_es_DEEP_general_rarity, color="en->es (Deep)")) +
  geom_line(aes(y=en_es_DEEPL_general_rarity, color="en->es (DeepL)")) +
  geom_line(aes(y=en_es_GOOGLE_general_rarity, color="en->es (GT)")) +
  geom_line(aes(y=en_es_TRANSFORMERS_general_rarity, color="en->es (OPUS)")) +
  labs(title="Common Vocab Size vs. General Rarity",
       x="Common Vocab Size",
       y="General Rarity",
       color="Language")
```

```{r ar_rarity_over_time}

df <- read_csv("corpus_level/rarity_different_vocab_sizes_summary.csv")

df <- df[, c("val", "ar_general_rarity",
             "en_ar_DEEP_general_rarity", 
             "en_ar_DEEPL_general_rarity",
             "en_ar_GOOGLE_general_rarity",
             "en_ar_TRANSFORMERS_general_rarity")]

ggplot(df, aes(x=val)) +
  geom_line(aes(y=ar_general_rarity, color="Native")) +
  geom_line(aes(y=en_ar_DEEP_general_rarity, color="en->ar (Deep)")) +
  geom_line(aes(y=en_ar_DEEPL_general_rarity, color="en->ar (DeepL)")) +
  geom_line(aes(y=en_ar_GOOGLE_general_rarity, color="en->ar (GT)")) +
  geom_line(aes(y=en_ar_TRANSFORMERS_general_rarity, color="en->ar (OPUS)")) +
  labs(title="Common Vocab Size vs. General Rarity",
       x="Common Vocab Size",
       y="General Rarity",
       color="Language")
```