---
title: "Count Data Linguistic Analysis"
author: "Dagmar Heintze"
date: "2024-09-10"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
#Set a Cran monitor
options(repos = c(CRAN = "https://cran.r-project.org"))
setwd("/Users/Dagmar Heintze/Desktop/R-Directory")
install.packages("ggplot2")
library(ggplot2)
```

#Ensure long format \# Load the tidyr package for converting to long
format #load relevant library

```{r}
library(tidyr)
```

#########Count Analyses for Arabic########## #Import the data

```{r}
ar_count_data <- read.csv("/Users/Dagmar Heintze/Downloads/ar_counts.csv")
View(ar_count_data)
```

#Transform to long table and select variables \# Lemma counts

```{r}
df_lemma_long <- pivot_longer(ar_count_data, 
                              cols = c(ar_lemma_counts,
                                       en_ar_DEEP_lemma_counts,
                                       en_ar_DEEPL_lemma_counts,
                                       en_ar_GOOGLE_lemma_counts,
                                       en_ar_TRANSFORMERS_lemma_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# AR Lemma counts

```{r}
ggplot(df_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR Lemma Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables \# Verb counts

```{r}
df_verb_long <- pivot_longer(ar_count_data, 
                              cols = c(ar_verb_counts,
                                       en_ar_DEEP_verb_counts,
                                       en_ar_DEEPL_verb_counts,
                                       en_ar_GOOGLE_verb_counts,
                                       en_ar_TRANSFORMERS_verb_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# AR Verb counts

```{r}
ggplot(df_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR Verb Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables \# Noun counts

```{r}
df_noun_long <- pivot_longer(ar_count_data, 
                              cols = c(ar_noun_counts,
                                       en_ar_DEEP_noun_counts,
                                       en_ar_DEEPL_noun_counts,
                                       en_ar_GOOGLE_noun_counts,
                                       en_ar_TRANSFORMERS_noun_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# AR Noun counts

```{r}
ggplot(df_noun_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR Noun Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End Count Analysis Arabic

######### Count Analyses for English

#Import the data

```{r}
en_count_data <- read.csv("/Users/Dagmar Heintze/Downloads/en_counts.csv")
View(en_count_data)
```

######### Analysis for ES-EN

#Transform to long table and select variables \# Lemma counts ES-EN

```{r}
df_es_en_lemma_long <- pivot_longer(en_count_data, 
                              cols = c(en_lemma_counts,
                                       es_en_DEEP_lemma_counts,
                                       es_en_DEEPL_lemma_counts,
                                       es_en_GOOGLE_lemma_counts,
                                       es_en_TRANSFORMERS_lemma_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# ES-EN Lemma counts 

```{r}
ggplot(df_es_en_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES-EN Lemma Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# ES-EN Verb counts 

```{r}
df_es_en_verb_long <- pivot_longer(en_count_data, 
                             cols = c(en_verb_counts,
                                      es_en_DEEP_verb_counts,
                                      es_en_DEEPL_verb_counts,
                                      es_en_GOOGLE_verb_counts,
                                      es_en_TRANSFORMERS_verb_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# ES-EN Verb counts 

```{r}
ggplot(df_es_en_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES-EN Verb Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables \# Noun counts ES-EN

```{r}
df_es_en_verb_long <- pivot_longer(en_count_data, 
                             cols = c(en_noun_counts,
                                      es_en_DEEP_noun_counts,
                                      es_en_DEEPL_noun_counts,
                                      es_en_GOOGLE_noun_counts,
                                      es_en_TRANSFORMERS_noun_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# ES-EN Noun counts 

```{r}
ggplot(df_es_en_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES-EN Noun Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

############ Analysis for AR-EN

#Transform to long table and select variables 
# AR-EN Lemma counts 

```{r}
df_ar_en_lemma_long <- pivot_longer(en_count_data, 
                                    cols = c(en_lemma_counts,
                                             ar_en_DEEP_lemma_counts,
                                             ar_en_DEEPL_lemma_counts,
                                             ar_en_GOOGLE_lemma_counts,
                                             ar_en_TRANSFORMERS_lemma_counts),
                                    names_to = "Variable", 
                                    values_to = "Value")
```

# Create the violin plot

# AR-EN Lemma counts

```{r}
ggplot(df_ar_en_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR-EN Lemma Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# AR-EN Verb counts 

```{r}
df_ar_en_verb_long <- pivot_longer(en_count_data, 
                                   cols = c(en_verb_counts,
                                            ar_en_DEEP_verb_counts,
                                            ar_en_DEEPL_verb_counts,
                                            ar_en_GOOGLE_verb_counts,
                                            ar_en_TRANSFORMERS_verb_counts),
                                   names_to = "Variable", 
                                   values_to = "Value")
```

# Create the violin plot

# AR-EN Verb counts 

```{r}
ggplot(df_es_en_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "Ar-EN Verb Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# AR-EN Noun counts 

```{r}
df_ar_en_verb_long <- pivot_longer(en_count_data, 
                                   cols = c(en_noun_counts,
                                            ar_en_DEEP_noun_counts,
                                            ar_en_DEEPL_noun_counts,
                                            ar_en_GOOGLE_noun_counts,
                                            ar_en_TRANSFORMERS_noun_counts),
                                   names_to = "Variable", 
                                   values_to = "Value")

```

# Create the violin plot

# AR-EN Noun counts 

```{r}
ggplot(df_es_en_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "Ar-EN Noun Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End Count Analyses for English

########## Count Analyses for Spanish

#Import the data

```{r}
es_count_data <- read.csv("/Users/Dagmar Heintze/Downloads/es_counts.csv")
View(es_count_data)
```

#Transform to long table and select variables 

# ES Lemma counts

```{r}
df_es_lemma_long <- pivot_longer(es_count_data, 
                              cols = c(es_lemma_counts,
                                       en_es_DEEP_lemma_counts,
                                       en_es_DEEPL_lemma_counts,
                                       en_es_GOOGLE_lemma_counts,
                                       en_es_TRANSFORMERS_lemma_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# ES Lemma counts

```{r}
ggplot(df_es_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES Lemma Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# ES Verb counts

```{r}
df_es_verb_long <- pivot_longer(es_count_data, 
                             cols = c(es_verb_counts,
                                      en_es_DEEP_verb_counts,
                                      en_es_DEEPL_verb_counts,
                                      en_es_GOOGLE_verb_counts,
                                      en_es_TRANSFORMERS_verb_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# ES Verb counts

```{r}
ggplot(df_es_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES Verb Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# ES Noun counts

```{r}
df_es_noun_long <- pivot_longer(es_count_data, 
                             cols = c(es_noun_counts,
                                      en_es_DEEP_noun_counts,
                                      en_es_DEEPL_noun_counts,
                                      en_es_GOOGLE_noun_counts,
                                      en_es_TRANSFORMERS_noun_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# ES Noun counts

```{r}
ggplot(df_es_noun_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES Noun Counts", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End Count Analysis Spanish

######### Begin Count Difference Analysis from Arabic

#Import the data

```{r}
ar_diff_data <- read.csv("/Users/Dagmar Heintze/Downloads/from_ar_counts_difference.csv")
View(ar_diff_data)
```

#Transform to long table and select variables 
# AR-EN Lemma difference 

```{r}
df_ar_diff_lemma_long <- pivot_longer(ar_diff_data, 
                                    cols = c(ar_en_DEEP_difference_lemma_counts,
                                             ar_en_DEEPL_difference_lemma_counts,
                                             ar_en_GOOGLE_difference_lemma_counts,
                                          ar_en_TRANSFORMERS_difference_lemma_counts),
                                    names_to = "Variable", 
                                    values_to = "Value")
```

# Create the violin plot

# AR-EN Lemma counts differnce 

```{r}
ggplot(df_ar_diff_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR-EN Lemma Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# AR-EN Verb counts Difference


```{r}
df_ar_diff_verb_long <- pivot_longer(ar_diff_data, 
                                   cols = c(
                                            ar_en_DEEP_difference_verb_counts,
                                            ar_en_DEEPL_difference_verb_counts,
                                            ar_en_GOOGLE_difference_verb_counts,
                                            ar_en_TRANSFORMERS_difference_verb_counts),
                                   names_to = "Variable", 
                                   values_to = "Value")
```

# Create the violin plot

# AR-EN Verb counts Difference 

```{r}
ggplot(df_ar_diff_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "Ar-EN Verb Count Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 

# AR-EN Noun counts Difference


```{r}
df_ar_diff_verb_long <- pivot_longer(ar_diff_data, 
                                   cols = c(
                                            ar_en_DEEP_difference_noun_counts,
                                            ar_en_DEEPL_difference_noun_counts,
                                            ar_en_GOOGLE_difference_noun_counts,
                                            ar_en_TRANSFORMERS_difference_noun_counts),
                                   names_to = "Variable", 
                                   values_to = "Value")

```

# Create the violin plot

# AR-EN Noun counts Difference

```{r}
ggplot(df_ar_diff_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "Ar-EN Noun Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c( "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End Count Difference Analysis Arabic ##############

########## Begin Count Difference Analysis English ##########

#Import the data

```{r}
en_diff_data <- read.csv("/Users/Dagmar Heintze/Downloads/en_counts_difference.csv")
View(en_diff_data)
```

#Transform to long table and select variables 
# ES-EN Lemma counts Difference

```{r}
df_es_en_diff_lemma_long <- pivot_longer(en_diff_data, 
                              cols = c(
                                       es_en_DEEP_difference_lemma_counts,
                                       es_en_DEEPL_difference_lemma_counts,
                                       es_en_GOOGLE_difference_lemma_counts,
                                       es_en_TRANSFORMERS_difference_lemma_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# ES-EN Lemma counts Difference

```{r}
ggplot(df_es_en_diff_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES-EN Lemma Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# ES-EN Verb counts Difference

```{r}
df_es_en_diff_verb_long <- pivot_longer(en_diff_data, 
                             cols = c(
                                      es_en_DEEP_difference_verb_counts,
                                      es_en_DEEPL_difference_verb_counts,
                                      es_en_GOOGLE_difference_verb_counts,
                                      es_en_TRANSFORMERS_difference_verb_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# ES-EN Verb counts difference

```{r}
ggplot(df_es_en_diff_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES-EN Verb Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# ES-EN Noun counts difference

```{r}
df_es_en_diff_noun_long <- pivot_longer(en_diff_data, 
                             cols = c(
                                      es_en_DEEP_difference_noun_counts,
                                      es_en_DEEPL_difference_noun_counts,
                                      es_en_GOOGLE_difference_noun_counts,
                                      es_en_TRANSFORMERS_difference_noun_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# ES-EN Noun counts difference

```{r}
ggplot(df_es_en_diff_noun_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "ES-EN Noun Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End ES-EN Count Difference Analysis

######### Beginning AR-EN Count Difference Analysis

#Transform to long table and select variables 
# AR-EN Lemma counts Difference

```{r}
df_ar_en_diff_lemma_long <- pivot_longer(en_diff_data, 
                              cols = c(
                                       ar_en_DEEP_difference_lemma_counts,
                                       ar_en_DEEPL_difference_lemma_counts,
                                       ar_en_GOOGLE_difference_lemma_counts,
                                       ar_en_TRANSFORMERS_difference_lemma_counts),
                              names_to = "Variable", 
                              values_to = "Value")
```

# Create the violin plot

# AR-EN Lemma counts Difference

```{r}
ggplot(df_ar_en_diff_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR-EN Lemma Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# AR-EN Verb counts difference

```{r}
df_ar_en_diff_verb_long <- pivot_longer(en_diff_data, 
                             cols = c(
                                      ar_en_DEEP_difference_verb_counts,
                                      ar_en_DEEPL_difference_verb_counts,
                                      ar_en_GOOGLE_difference_verb_counts,
                                      ar_en_TRANSFORMERS_difference_verb_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# AR-EN Verb counts difference

```{r}
ggplot(df_ar_en_diff_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "Ar-EN Verb Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# AR-EN Noun counts Difference

```{r}
df_ar_en_diff_noun_long <- pivot_longer(en_diff_data, 
                             cols = c(
                                      ar_en_DEEP_difference_noun_counts,
                                      ar_en_DEEPL_difference_noun_counts,
                                      ar_en_GOOGLE_difference_noun_counts,
                                      ar_en_TRANSFORMERS_difference_noun_counts),
                             names_to = "Variable", 
                             values_to = "Value")
```

# Create the violin plot

# AR-EN Noun counts Difference

```{r}
ggplot(df_ar_en_diff_noun_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "AR-EN Noun Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("Gold Standard", "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End AR-EN Count Difference Analysis #############

######### Begin Count Difference Analysis from Spanish ##########

#Import the data

```{r}
es_diff_data <- read.csv("/Users/Dagmar Heintze/Downloads/es_counts_difference.csv")
View(es_diff_data)
```

#Transform to long table and select variables 

# EN-ES Lemma count Difference 

```{r}
df_es_diff_lemma_long <- pivot_longer(es_diff_data, 
                                    cols = c(en_es_DEEP_difference_lemma_counts,
                                             en_es_DEEPL_difference_lemma_counts,
                                             en_es_GOOGLE_difference_lemma_counts,
                                          en_es_TRANSFORMERS_difference_lemma_counts),
                                    names_to = "Variable", 
                                    values_to = "Value")
```

# Create the violin plot

# EN-ES Lemma counts differnce 

```{r}
ggplot(df_es_diff_lemma_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "EN-ES Lemma Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 

# EN-ES Verb counts Difference


```{r}
df_es_diff_verb_long <- pivot_longer(es_diff_data, 
                                   cols = c(
                                            en_es_DEEP_difference_verb_counts,
                                            en_es_DEEPL_difference_verb_counts,
                                            en_es_GOOGLE_difference_verb_counts,
                                            en_es_TRANSFORMERS_difference_verb_counts),
                                   names_to = "Variable", 
                                   values_to = "Value")
```

# Create the violin plot

# EN-ES Verb counts Difference 

```{r}
ggplot(df_es_diff_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "EN-ES Verb Count Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c("DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

#Transform to long table and select variables 
# EN-ES Noun counts Difference

```{r}
df_es_diff_verb_long <- pivot_longer(es_diff_data, 
                                   cols = c(
                                            en_es_DEEP_difference_noun_counts,
                                            en_es_DEEPL_difference_noun_counts,
                                            en_es_GOOGLE_difference_noun_counts,
                                            en_es_TRANSFORMERS_difference_noun_counts),
                                   names_to = "Variable", 
                                   values_to = "Value")

```

# Create the violin plot

# EN-ES Noun counts Difference

```{r}
ggplot(df_es_diff_verb_long, aes(x = Variable, y = Value, fill = Variable)) +
  geom_violin(trim = FALSE, color = "black") +
  theme_minimal() +
  labs(title = "EN-ES Noun Counts Difference", y = "Value") +
  theme(legend.position = "none") +  
  scale_x_discrete(labels = c( "DEEP", "DEEPL", "GOOGLE", "TRANSFORMERS"))  # Custom x-axis labels
```

######### End Count Difference Analysis Spanish #########